---
output: github_document
---


# Multi-Objective Optimization Repository (MOrepo)

This repository is a response to the needs of researchers from the MCDM society to access multi-objective (MO) optimization instances. The repository contains instances, generators and algorithms for different MO problems and is continusly updated. The repository can be used as a test set for testing new algorithms, validating existing results and for reproducibility. All resarchers within MO optimization are welcome to contribute. 

## Usage

Instances can be downloaded in different ways depending on usage:

   - If you want the whole repository, download it as a zip file
   - Browse to a single instance and download it using the raw format at GitHub
   - Use the R package `MOrepoTools` to download instances
   
We recormend the last option and illustrate how it works. You don't need much knowledge about R to use the package. But of course it is preferable. You need [R](https://www.r-project.org/) and preferable [RStudio](https://www.rstudio.com/) installed on your computer. First you have to install the `MOrepoTools` package. From the R commandline write:

```{r}
library(devtools)   # 
install_github()
```

Now download instances and results using 

```{r}
getInstanceInfo(...)
getInstance(...)
```



## Features

The repository mainly contains MO test instanses from variaous sources. However, also generator, algorithms and other source code related to MO optimization are welcome. 

## Structure

Dir structure


## Instance format 

 
 - Free MPS format
 - Raw with desc




## Solution format (JSON?)

A file named <instance_name>_sol<number>.json



instance: name of instance (string)
comments: misc comments about the results (string, null)
nDCard: Total number/cardinality of nondominated points (number, null)
suppCard: Number of supported nondominated points (number, null)
extCard: Number of extreme supported nondominated points (number, null)
critType: array of integer, real, null with length as number of criteria (array, null)
points: Array with nondominated points objects 0(array, null)
   
   A point object consists of 
   class: either us (unsupported), se (supported extreme), s (supported - may be extreme or nonextreme), sne (supported nonextreme), null (unknown)
   point: array of numbers
   
 (eller måske pointsClass i stedet for?)
optimal: (true, false, null)






## Validators


R package

- check a contribution
- download a set of test instances
- download solutions and plot
- download citation
- merge ndsets



## Problem classification
 
Instances are classified into different classifications. This set is expanded as new problem instances is added to the repository. The current classifications of MO optimization problems are 

- Knapsack
- Assignment   
- Traveling salesman (TSP)
- Setcovering
- Setpartitioning
- Setpacking 
- Facility location
- Shortest path
- Transhipment
- Multi-commodity flow
- Minimum cost network flow
- IP/MILP (general problems with a mixture of constraints)  

 
 
## Instance numbering


## Biblography


## How to contribute


## Contributors
  




The MCDM society would benefit from a joint multi-objective optimization repository with MOO instances and algorithms. In this talk we will present our ideas about the open-source Multi-Objective Optimization Repository (MOPR) and give an overview over current features and progress. The talk is also open for discussion about feature requests etc. 
