---
output: 
   github_document:
      html_preview: true
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
library(MOrepoTools)
library(bibtex)
library(kableExtra)
knitr::opts_chunk$set(opts=list(blank=FALSE, width.cutoff=120), cache = FALSE, 
                      autodep = TRUE, collapse=TRUE, error = FALSE)
knitr::opts_knit$set(width = 90)
```

```{r How to update the repo (done using GitHub actions), eval=FALSE, echo=FALSE}
MOrepoTools:::setMetaContributions()
for(i in 1:10){
   try({
     r <- MOrepoTools:::setMetaInstances()
     break
   }, silent = FALSE)
}
for(i in 1:10){
   try({
     r <- MOrepoTools:::setMetaResults()
     break
   }, silent = FALSE)
}
```


# Multi-Objective Optimization Repository (MOrepo)

This repository is a response to the needs of researchers from the MCDM society to access multi-objective (MO) optimization instances. The repository contains instances, results, generators etc. for different MO problems and is continuously updated. The repository can be used as a test set for testing new algorithms, validating existing results and for reproducibility. All researchers within MO optimization are welcome to contribute. 

The repository consists of a main repository [`MOrepo`](https://github.com/MCDMSociety/MOrepo) at GitHub and a set of sub-repositories, one for each contribution. Sub-repositories are named `MOrepo-<name>` where `name` normally is the surname of the first author and year of the study. All repositories are located within the [`MCDMSociety`](https://github.com/MCDMSociety/) organization at GitHub. 

The main repository contains documentation about how to use and contribute to `MOrepo`. Moreover, a set of tools are given in the R package `MOrepoTools` which can be used to retrieve info about test instance groups, results and problem classes. 

Maintainers of `MOrepo` are Lars Relund Nielsen <larsrn@econ.au.dk> and Sune Gadegaard <sgadegaard@econ.au.dk>. 

Current maintainers of sub-repositories are `r vec2String(getMaintainers())`.

Current contributors to the repository are `r vec2String(getContributorNames())`. 

## Usage

Instances can be downloaded in different ways depending on usage:

   - If you want a whole sub-repository, download it as a zip file or clone it on GitHub.
   - Browse to a single instance and download it using the raw format at GitHub.
   - Use the R package `MOrepoTools` to download instances.

All researchers are welcome to contribute to `MOrepo`. The repository mainly contains MO test instances and results from various sources. However, also generators, format converters, algorithms etc. related to MO optimization are welcome. Have a look at the [contribute file](contribute.md) which describes different ways to do it. 

## Test instances @ MOrepo

```{r, include=FALSE}
dat <- getProblemClasses()
```

MOrepo contains instances for different problem classes. The contributions listed after class are:

```{r, results='asis', echo=FALSE, tidy=FALSE}
tab <- tibble::tibble("Problem class" = NA_character_, "Repository" = NA_character_, .rows = 0)
for (i in dat) {
   res <- getInstanceInfo(class = i, silent = TRUE)
   repo <- stringr::str_c("[", purrr::map_chr(res, function(x) x$contributionName), "]")
   url <- stringr::str_c("(", "https://github.com/MCDMSociety/MOrepo-", names(res), ")")
   str <- stringr::str_c(repo, url, collapse = ", ")
   tab <- dplyr::bind_rows(tab, c(`Problem class` = i, Repository = str))
}
kbl(tab, format = "pipe")
```

### Detailed information

MOrepo contains instances for problem classes `r vec2String(dat)`. A detailed description of the contributions are:

```{r, results='asis', echo=FALSE, tidy=FALSE}
getInstanceInfo(withLinks = TRUE)
```


## Results @ MOrepo

MOrepo contains results for some of the instances in problem classes:

```{r, include=FALSE}
dat <- getProblemClasses(results = TRUE)
```

```{r, results='asis', echo=FALSE, tidy=FALSE}
tab <- tibble::tibble("Problem class" = NA_character_, "Repository" = NA_character_, .rows = 0)
for (i in dat) {
   res <- getResultInfo(class = i, silent = TRUE)
   repo <- stringr::str_c("[", purrr::map_chr(res, function(x) x$contributionName), "]")
   url <- stringr::str_c("(", "https://github.com/MCDMSociety/MOrepo-", names(res), ")")
   str <- stringr::str_c(repo, url, collapse = ", ")
   tab <- dplyr::bind_rows(tab, c(`Problem class` = i, Repository = str))
}
kbl(tab, format = "pipe")
```

### Detailed information

MOrepo contains results for some of the instances in problem classes `r vec2String(dat)`. The contributions are:

```{r, results='asis', echo=FALSE, tidy=FALSE}
getResultInfo(withLinks = TRUE)
```


## How to cite

To cite use 

```
@Electronic{MOrepo,
  Title                    = {Multi-Objective Optimization Repository (MOrepo)},
  Author                   = {L. R. Nielsen},
  Url                      = {https://github.com/MCDMSociety/MOrepo},
  Year                     = {2017}
}
```


## Use R to download instances
   
You may use the R package `MOrepoTools` to download instances. You don't need much knowledge about R to use the package. But of course it is preferable. You need [R](https://www.r-project.org/) and preferable [RStudio](https://www.rstudio.com/) installed on your computer. First you have to install the `MOrepoTools` package. From the R command line write:

```{r, eval=FALSE}
library(devtools)   # if the package is missing see ?install.package 
install_github("MCDMSociety/MOrepo/misc/R/MOrepoTools")
```

To get an overview over the current problem classes run:

```{r}
library(MOrepoTools)
getProblemClasses()  # current problem classes in MOrepo
getInstanceInfo(class = "Assignment")  # info about instances for the assignment problem
```

Now download the Tuyttens00 contribution as a zip file using 

```{r, cache=TRUE}
getContributionAsZip("Tuyttens00")
```





