---
output: github_document
---

```{r, include=FALSE}
library(MOrepoTools)
knitr::opts_chunk$set(tidy = TRUE, opts=list(blank=FALSE, width.cutoff=120), cache = FALSE, 
                      autodep = TRUE, collapse=TRUE)
knitr::opts_knit$set(width = 90)
```


# Multi-Objective Optimization Repository (MOrepo)

This repository is a response to the needs of researchers from the MCDM society to access multi-objective (MO) optimization instances. The repository contains instances, results, generators etc. for different MO problems and is continuously updated. The repository can be used as a test set for testing new algorithms, validating existing results and for reproducibility. All researchers within MO optimization are welcome to contribute. 

The repository consists of a main repository [`MOrepo`](https://github.com/MCDMSociety/MOrepo) at GitHub and a set of sub-repositories, one for each contribution. Sub-repositories are named `MOrepo-<name>` where `name` normally is the surname of the first author and year of the study. All repositories are located within the [`MCDMSociety`](https://github.com/MCDMSociety/) organization at GitHub. 

The main repository contains documentation about how to use and contribute to `MOrepo`. Moreover, a set of tools are given in the R package `MOrepoTools` which can be used to retrieve info about test instance groups, results and problem classes. 

<!-- - `instances` - A folder containing the instance sets. Each instance set in contained in a subfolder for each paper using the instances the first time. -->
<!-- - `results` - A folder containing results for the instances. Results may be a set of nondominated points (or an approximation), upper and lower bounds etc. Results are not stored in the `instances` folder since different papers may have results for the same instances. -->
<!-- - `misc` - A folder with stuff that cannot be included into the two folders above such as R packages, generators, converters etc.  -->

Maintainers of `MOrepo` are Lars Relund Nielsen <larsrn@econ.au.dk>, Sune Gadegaard <sgadegaard@econ.au.dk>, Thomas Stridsen <thst@dta.dk> and Kim Allan Andersen <kia@econ.au.dk>. 

Current maintainers of sub-repositories are `r vec2String(getMaintainers())`.

Current contributors to the repository are `r vec2String(getContributorNames())`. 


## Usage

Instances can be downloaded in different ways depending on usage:

   - If you want a whole sub-repository, download it as a zip file on GitHub.
   - Browse to a single instance and download it using the raw format at GitHub.
   - Use the R package `MOrepoTools` to download instances.
   
We recommend the last option and illustrate how it works. You don't need much knowledge about R to use the package. But of course it is preferable. You need [R](https://www.r-project.org/) and preferable [RStudio](https://www.rstudio.com/) installed on your computer. First you have to install the `MOrepoTools` package. From the R command line write:

```{r, eval=FALSE}
library(devtools)   # if the package is missing see ?install.package 
install_github("MCDMSociety/MOrepo/misc/R/MOrepoTools")
```


To get an overview over the current problem classes run:

```{r, cache=TRUE}
library(MOrepoTools)
getProblemClasses()  # current problem classes in MOrepo
getInstanceInfo(class = "Assignment")  # info about instances for the assignment problem
```

Now download the Tuyttens00 contribution as a zip file using 

```{r, cache=TRUE}
getContributionAsZip("Tuyttens00")
```

Or download selected instances 

```{r}
getInstance(name="Tuyttens.*n10")
```



## How to contribute

All researchers are welcome to contribute to `MOrepo`. The repository mainly contains MO test instances and results from various sources. However, also generators, format converters, algorithms etc. related to MO optimization are welcome. Have a look at the documentation file [`contribute.md`](contribute.md) which describes different ways to do it. 




```{r, include=FALSE}
dat <- getProblemClasses()
```

## Test instances @ MOrepo

Currently MOrepo contains instances for problem classes `r vec2String(dat)`. The contributions listed after class are:

```{r, results='asis', echo=FALSE, tidy=FALSE}
for (i in dat) {
   cat("\n### Problem class ", i, "\n")
   getInstanceInfo(class = i, withLinks = TRUE)
}
```

## Results @ MOrepo

```{r, include=FALSE}
dat <- getProblemClasses(results = TRUE)
```

Currently MOrepo contains results for instances in problem classes `r vec2String(dat)`. The contributions listed after class are:

```{r, results='asis', echo=FALSE, tidy=FALSE}
for (i in dat) {
   cat("\n### Problem class ", i, "\n")
   getResultInfo(class = i, withLinks = TRUE)
}
```


<!-- 
 
 - Free MPS format

## Validators


R package

- check a contribution
- download a set of test instances
- download solutions and plot
- download citation
- merge ndsets


The MCDM society would benefit from a joint multi-objective optimization repository with MOO instances and algorithms. In this talk we will present our ideas about the open-source Multi-Objective Optimization Repository (MOPR) and give an overview over current features and progress. The talk is also open for discussion about feature requests etc.   -->
